---
title: Coffee Ratings
author: "percentage-%"
output: github_document
---

## Summary

Information of dataset

Nowadays people are more and more getting used to having a cup of coffee in the morning to start the day. Therefore, an increasing amount of coffee lovers are attempting to research the quality of coffees, so that higher quality of coffee can be provided to the world. In order to find out how the quality of coffee can be related to other factors such as species, or altitude. We are employing the database from TidyTuesday with the source James LeDoux & Coffee Quality Database, and we will reorganize the collected data and import it into GitHub and use R studio to program ggplot for analysis. 

We are assuming that various variables such as the species, country of origin, and color of coffee samples might have the possibility to exploit the quality of the coffee. Therefore, we’ve selected the following variables from the data, including "total_cup_points", "species", "country_of_origin", "company", "altitude”, "harvest_year", "processing_method”, "variety", "color", "moisture". And in turn, explore whether there is a relationship between every single variable and total cup points while controlling other variables unchanged.

Research Question
Exploring the correlation between processing method and total cup points, and what other variables we choose will influence the total cup points under the same circumstance of processing method.

Methodology
There are a total of eight variables, there are four of us, each person is assigned two variables, and then we will use scatter plots and histograms to represent our discoveries from the datasets the, in order to find out the relationship between total cup points of each variable under the same processing method.

Finding
According to our analysis of data,Variables like processing method, altitude, variety, species, moisture and country of origin do impact the total cup points of coffee, which means If you want to choose good quality coffee, you should choose coffee with specific variables,such as honey processing method way and Ethiopia origin to get a good one.


# Coffee Ratings
The data this week comes from James LeDoux & Coffee Quality Database (https://github.com/jldbc/coffee-quality-database). 
This Yorgos Askalidis - TWD (https://towardsdatascience.com/the-data-speak-ethiopia-has-the-best-coffee-91f88ed37e84) talks about Coffee Ratings in greater detail.
Credit: %(Percentage) 


```{r load-data, echo = FALSE}
coffee_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-07/coffee_ratings.csv')
```

```{r Cleaning Script, echo = FALSE}
library(tidyverse)

raw_arabica <- read_csv("https://raw.githubusercontent.com/jldbc/coffee-quality-database/master/data/arabica_data_cleaned.csv") %>% 
  janitor::clean_names()

raw_robusta <- read_csv("https://raw.githubusercontent.com/jldbc/coffee-quality-database/master/data/robusta_data_cleaned.csv",
                        col_types = cols(
                          X1 = col_double(),
                          Species = col_character(),
                          Owner = col_character(),
                          Country.of.Origin = col_character(),
                          Farm.Name = col_character(),
                          Lot.Number = col_character(),
                          Mill = col_character(),
                          ICO.Number = col_character(),
                          Company = col_character(),
                          Altitude = col_character(),
                          Region = col_character(),
                          Producer = col_character(),
                          Number.of.Bags = col_double(),
                          Bag.Weight = col_character(),
                          In.Country.Partner = col_character(),
                          Harvest.Year = col_character(),
                          Grading.Date = col_character(),
                          Owner.1 = col_character(),
                          Variety = col_character(),
                          Processing.Method = col_character(),
                          Fragrance...Aroma = col_double(),
                          Flavor = col_double(),
                          Aftertaste = col_double(),
                          Salt...Acid = col_double(),
                          Balance = col_double(),
                          Uniform.Cup = col_double(),
                          Clean.Cup = col_double(),
                          Bitter...Sweet = col_double(),
                          Cupper.Points = col_double(),
                          Total.Cup.Points = col_double(),
                          Moisture = col_double(),
                          Category.One.Defects = col_double(),
                          Quakers = col_double(),
                          Color = col_character(),
                          Category.Two.Defects = col_double(),
                          Expiration = col_character(),
                          Certification.Body = col_character(),
                          Certification.Address = col_character(),
                          Certification.Contact = col_character(),
                          unit_of_measurement = col_character(),
                          altitude_low_meters = col_double(),
                          altitude_high_meters = col_double(),
                          altitude_mean_meters = col_double()
                        )) %>% 
  janitor::clean_names() %>% 
  rename(acidity = salt_acid, sweetness = bitter_sweet,
         aroma = fragrance_aroma, body = mouthfeel,uniformity = uniform_cup)


all_ratings <- bind_rows(raw_arabica, raw_robusta) %>% 
  select(-x1) %>% 
  select(total_cup_points, species, everything())

all_ratings %>% 
  skimr::skim()

all_ratings %>% 
  write_csv("coffee_ratings.csv")
```

## Presentation

Our presentation can be found [here](https://media.ed.ac.uk/media/percentage-coffee+ratings/1_558ng9sa)

slides is: https://u-edinburgh.rstudio.cloud/23d6b421b9244e50bc6557c7b29ee967/file_show?path=%2Fcloud%2Fproject%2Fpresentation%2Fpresentation.html#1


## Data 

Askalidis, Y. (2019, March 26). The data is in: Ethiopia has the best coffee. Retrieved October 23, 2020, from https://towardsdatascience.com/the-data-speak-ethiopia-has-the-best-coffee-91f88ed37e84

LeDoux, J. (2018, June 17). Jldbc/coffee-quality-database. Retrieved October 23, 2020, from https://github.com/jldbc/coffee-quality-database


## References

James LeDoux & Coffee Quality Database (https://github.com/jldbc/coffee-quality-database). 
Yorgos Askalidis - TWD (https://towardsdatascience.com/the-data-speak-ethiopia-has-the-best-coffee-91f88ed37e84) 
