---
title: "Coffee Ratings"
subtitle: "linear relationship between each single variable and total cup points"
author: "Percentage(Ziling Luo, Qi Qiu, Betty Wang, Shizhao Xiong) "
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(xaringan)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
tuesdata <- tidytuesdayR::tt_load('2020-07-07')
tuesdata <- tidytuesdayR::tt_load(2020, week = 28)

coffee_ratings <- tuesdata$coffee_ratings

coffee_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-07/coffee_ratings.csv')
```


class: center, middle

## Exploring the correlation between processing method and total cup points.

---

class: inverse, center, middle

# Section title

---

# Hello World

- Click the `Knit` button to compile your presentation

- Make sure to commit and push all resulting files to your GitHub repo

---

class: inverse, middle, center

# Using xaringan

---


# Layouts

You can use plain text

- or bullet points

.pull-left[
or text in two columns $^*$
]
.pull-right[
- like
- this
]

.footnote[
percentage(%)
]

---

# Plots

```{r recode-species, echo = FALSE}
# In this chunk I'm doing a bunch of analysis that I don't want to present 
# in my slides. But I need the resulting data frame for a plot I want to present.
iris_modified <- iris %>%
  mutate(Species = fct_other(Species, keep = "setosa"))
```

```{r plot-iris, echo = FALSE, fig.height = 2.5, fig.width = 5}
# Code hidden with echo = FALSE
# Uses modified iris dataset from previous chunk
# Play around with height and width until you're happy with the look
ggplot(data = iris_modified, mapping = aes(x = Sepal.Width, y = Sepal.Length, color = Species)) +
  geom_point() + 
  theme_minimal() # theme options: https://ggplot2.tidyverse.org/reference/ggtheme.html
```

---

## Plot and text

.pull-left[
- Some text
- goes here
]
.pull-right[
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
]

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
kable(head(iris), format = "html")
```

---

# Images

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80")
```

Or you can also include a full page image. See next slide.


# Feeling adventurous?

- Want to find out more about `xaringan`? See https://slides.yihui.name/xaringan/#1.

- You are welcomed to use the default styling of the slides. In fact, that's what 
I expect majority of you will do. You will differentiate yourself with the content 
of your presentation.

- But some of you might want to play around with slide styling. The 
`xaringanthemer` provides some solutions for this that: https://pkg.garrickadenbuie.com/xaringanthemer/. 

---

class: inverse, middle, center

# Processing Method vs. Total Cup Points 
# By Species & Country of Origin 
# Qi(Emily) Qiu

---
# Species

```{r Emily-species-1, echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5, fig.align = "center",out.width="80%"}
# species
coffee_e <- coffee_ratings %>%
  select("processing_method","total_cup_points","species","country_of_origin")

coffee_e %>%
  ggplot(coffee_e, mapping = aes(x = processing_method,
             y = total_cup_points,
             color = species)) +
  geom_point(size = 0.8) +
  ylim(55,95) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

# Species

```{r Emily-species-2, echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}

coffee_e %>%
  mutate(
    processing_method = fct_infreq(processing_method)
  ) %>%
  ggplot(coffee_e, mapping = aes(x = processing_method,
             y = total_cup_points,
             color = species)) +
  facet_wrap(~ species) +
  geom_point(size = 0.7) +
  ylim(55,95) +
  theme_minimal() +
  guides(colour = FALSE) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

```


---
#Species

```{r Emily-species-3, echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}

coffee_e %>%
  mutate(
    processing_method = fct_infreq(processing_method)
  ) %>%
  filter(species == "Arabica") %>%
  ggplot(coffee_e, mapping = aes(x = processing_method,
             y = total_cup_points,
             color = species)) +
  facet_wrap(~ species) +
  geom_point(size = 0.7) +
  ylim(55,95) +
  theme_minimal() +
  guides(colour = FALSE) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

```
---
# Country of origin

```{r Emily-country_of_origin-1, echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}
# country of origin
coffee_e %>% 
  ggplot(coffee_e, mapping = aes(x = country_of_origin ,
             y = total_cup_points,
             color = processing_method)) +
  geom_point(size = 0.6) +
  ylim(55,95) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 7, angle = 70, hjust = 1))
```

---
# Country of origin
```{r Emily-country_of_origin-2, echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}
# country of origin
coffee_e %>% 
  mutate(
    country_of_origin = fct_infreq(country_of_origin)
  ) %>%
  filter(processing_method == "Washed / Wet") %>%
  ggplot(coffee_e, mapping = aes(x = country_of_origin ,
             y = total_cup_points,
             colour = processing_method)) +
  labs(
    title = "Processing method -- Washed / Wet"
  ) +
  geom_point(size = 0.6) +
  ylim(55,95) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 7, angle = 70, hjust = 1))
```
---
# Country of origin
```{r Emily-country_of_origin-3, echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}
# country of origin
coffee_e %>% 
  mutate(
    country_of_origin = fct_infreq(country_of_origin)
  ) %>%
  filter(processing_method == "Natural / Dry") %>%
  ggplot(coffee_e, mapping = aes(x = country_of_origin ,
             y = total_cup_points,
             colour = processing_method)) +
  labs(
    title = "Processing method -- Natural / Dry"
  ) +
  geom_point(size = 0.6) +
  ylim(55,95) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 7, angle = 70, hjust = 1))
```
---

# Relationship between virable processing method and total cup points
```{r echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}
# processing method
ziling_coffee <- coffee_ratings %>%
  filter(altitude_mean_meters <= 4287&!is.na(processing_method)) %>%
  select("total_cup_points","company","altitude_mean_meters","processing_method")

ziling_coffee %>%
  ggplot(ziling_coffee, mapping = aes(x = processing_method, y = total_cup_points)) +
  geom_point(alpha = 0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 10, hjust = 1))
```

---
# Relationship between virable ailtitude and total cup points
```{r echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}
# altitude
ziling_coffee %>%
  ggplot(ziling_coffee, mapping = aes(x = altitude_mean_meters, y = total_cup_points, color = processing_method)) +
  ylim(55,95) +
  geom_point(size = 0.08) +
  theme_minimal() 
```

---
# Code

```{r Trixy—harvest_year}
# harvest year
coffee_a <- coffee_ratings %>%
  select("total_cup_points","harvest_year","variety","processing_method")

coffee_a %>%
  filter(harvest_year <=2018&harvest_year >=2009) %>%
  ggplot(coffee_a, mapping = aes(x = harvest_year, y = total_cup_points, color = processing_method)) +
  ylim(50,100) +
  geom_point(size = 0.08)
```

---

# Code

```{r Trixy-variety}
# variety
coffee_a %>%
  ggplot(coffee_a, mapping = aes(x = variety, y = total_cup_points, color = processing_method)) +
  ylim(55,95) +
  geom_point(size = 0.08)
```


---

# Relationship between virable moisture and total cup points

```{r warning=FALSE, out.width="80%", fig.width=5.5, echo=FALSE}
coffee_moisture <- coffee_ratings %>%
  select("total_cup_points","moisture","processing_method")

coffee_moisture %>%
filter(total_cup_points > 65) %>%
ggplot(aes(x = moisture , y = total_cup_points , color = processing_method)) + 
 geom_point()
```

---

# Relationship between virable moisture and total cup points

```{r warning=FALSE, out.width="80%", fig.width=6, echo=FALSE}
coffee_moisture <- coffee_ratings %>%
  select("total_cup_points","moisture","processing_method")

coffee_moisture %>%
 filter(total_cup_points > 65) %>%
  ggplot(aes(x = moisture, y = total_cup_points, color = processing_method)) +
  geom_point(size = 0.5) +
  facet_wrap(~ processing_method, scale = "free_y") + 
  theme(legend.position = "none")
```

---

# Relationship between virable color and total cup points

```{r warning=FALSE, out.width="80%", fig.width=6, echo=FALSE}
coffee_color <- coffee_ratings %>%
  select("total_cup_points","color","processing_method")

coffee_color %>%
  filter(total_cup_points > 65) %>%
  ggplot(aes(total_cup_points, fill = color )) +
  geom_histogram(binwidth = 2) +
  facet_wrap(~ processing_method, scale = "free_y") + 
  theme(legend.position = "none")
```

---
