---
title: "Coffee Ratings"
subtitle: "relationship between each single variable and total cup points"
author: "Percentage(Ziling Luo, Qi Qiu, Betty Wang, Shizhao Xiong)"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(xaringan)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
tuesdata <- tidytuesdayR::tt_load('2020-07-07')
tuesdata <- tidytuesdayR::tt_load(2020, week = 28)

coffee_ratings <- tuesdata$coffee_ratings

coffee_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-07/coffee_ratings.csv')
```

class: center, middle

# Research Question: 
## Exploring the correlation between processing method and total cup points, and what other variables we choose will influence the total cup points under the same circumstance of processing method.

---

class: inverse, middle, center

# How Processing Method & Altitude Influence Total Cup Points 
# Under Same Processing Method  
# Ziling Luo

---

# Relationship between variable processing method and total cup points

```{r echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}
# processing method
ziling_coffee <- coffee_ratings %>%
  filter(altitude_mean_meters <= 4287&!is.na(processing_method)) %>%
  select("total_cup_points","company","altitude_mean_meters","processing_method")

ziling_coffee %>%
  ggplot(ziling_coffee, mapping = aes(x = processing_method, y = total_cup_points)) +
  geom_point(alpha = 0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 10, hjust = 1))
```

---

# Relationship between variable altitude and total cup points

```{r echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}
# altitude
ziling_coffee %>%
  ggplot(ziling_coffee, mapping = aes(x = altitude_mean_meters, y = total_cup_points, color = processing_method)) +
  ylim(55,95) +
  geom_point(size = 0.08) +
  theme_minimal() 
```

---

class: inverse, middle, center

# How Species & Country of Origin Influence Total Cup Points 
# Under Same Processing Method 
# Qi(Emily) Qiu

---

# Species

```{r Emily-species-1, echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5, fig.align = "center",out.width="80%"}
# species
coffee_e <- coffee_ratings %>%
  select("processing_method","total_cup_points","species","country_of_origin")

coffee_e %>%
  ggplot(coffee_e, mapping = aes(x = processing_method,
             y = total_cup_points,
             color = species)) +
  geom_point(size = 0.8) +
  ylim(55,95) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

---

# Species

```{r Emily-species-2, echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}

coffee_e %>%
  mutate(
    processing_method = fct_infreq(processing_method)
  ) %>%
  ggplot(coffee_e, mapping = aes(x = processing_method,
             y = total_cup_points,
             color = species)) +
  facet_wrap(~ species) +
  geom_point(size = 0.7) +
  ylim(55,95) +
  theme_minimal() +
  guides(colour = FALSE) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

```

#Species

```{r Emily-species-3, echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}

coffee_e %>%
  mutate(
    processing_method = fct_infreq(processing_method)
  ) %>%
  filter(species == "Arabica") %>%
  ggplot(coffee_e, mapping = aes(x = processing_method,
             y = total_cup_points,
             color = species)) +
  facet_wrap(~ species) +
  geom_point(size = 0.7) +
  ylim(55,95) +
  theme_minimal() +
  guides(colour = FALSE) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

```

---

# Country of origin

```{r Emily-country_of_origin-1, echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}
# country of origin
coffee_e %>% 
  ggplot(coffee_e, mapping = aes(x = country_of_origin ,
             y = total_cup_points,
             color = processing_method)) +
  geom_point(size = 0.6) +
  ylim(55,95) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 7, angle = 70, hjust = 1))
```

---

# Country of origin

```{r Emily-country_of_origin-2, echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}
# country of origin
coffee_e %>% 
  mutate(
    country_of_origin = fct_infreq(country_of_origin)
  ) %>%
  filter(processing_method == "Washed / Wet") %>%
  ggplot(coffee_e, mapping = aes(x = country_of_origin ,
             y = total_cup_points,
             colour = processing_method)) +
  labs(
    title = "Processing method -- Washed / Wet"
  ) +
  geom_point(size = 0.6) +
  ylim(55,95) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 7, angle = 70, hjust = 1))
```

---

# Country of origin

```{r Emily-country_of_origin-3, echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}
# country of origin
coffee_e %>% 
  mutate(
    country_of_origin = fct_infreq(country_of_origin)
  ) %>%
  filter(processing_method == "Natural / Dry") %>%
  ggplot(coffee_e, mapping = aes(x = country_of_origin ,
             y = total_cup_points,
             colour = processing_method)) +
  labs(
    title = "Processing method -- Natural / Dry"
  ) +
  geom_point(size = 0.6) +
  ylim(55,95) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 7, angle = 70, hjust = 1))
```

---

class: inverse, middle, center

# How Harvest Year & Variety Influence Total Cup Points 
# Under Same Processing Method 
# Shizhao(Trixy) Xiong

---

# Relationship between variable harvest year and total cup points

```{r echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}
# harvest year
coffee_a <- coffee_ratings %>%
  select("total_cup_points","harvest_year","variety","processing_method")

coffee_a %>%
  filter(harvest_year <=2018&harvest_year >=2009) %>%
  ggplot(coffee_a, mapping = aes(x = harvest_year, y = total_cup_points, color = processing_method)) +
  ylim(50,100) +
  geom_point(size = 0.08) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 5, angle = 40, hjust = 1))
```

---

```{r echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}
# harvest year
coffee_a <- coffee_ratings %>%
  select("total_cup_points","harvest_year","variety","processing_method")

coffee_a %>%
  filter(harvest_year <=2018&harvest_year >=2009) %>%
  ggplot(coffee_a, mapping = aes(x = harvest_year, y = total_cup_points, color = processing_method)) +
  ylim(50,100) +
  geom_point(size = 0.5) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 5, angle = 80, hjust = 1)) +
  facet_wrap(~ processing_method, scale = "free_y") + 
  theme(legend.position = "none")
```

---

# Relationship between variable variety and total cup points

```{r echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}
# variety
coffee_a %>%
  ggplot(coffee_a, mapping = aes(x = variety, y = total_cup_points, color = processing_method)) +
  ylim(55,95) +
  geom_point(size = 0.08) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 5, angle = 80, hjust = 1))
```

---

```{r echo = FALSE, warning=FALSE, fig.height = 2.5, fig.width = 5,fig.align = "center",out.width="80%"}
# variety
coffee_a %>%
  ggplot(coffee_a, mapping = aes(x = variety, y = total_cup_points, color = processing_method)) +
  ylim(55,95) +
  geom_point(size = 0.08) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 5, angle = 80, hjust = 1)) +
  facet_wrap(~ processing_method, scale = "free_y") + 
  theme(legend.position = "none")
```

---

class: inverse, middle, center

# How Moisture & Color Influence Total Cup Points 
# Under Same Processing Method 
# Betty Wang

---

# Relationship between moisture and total cup points

```{r warning=FALSE, out.width="80%", fig.width=5.5, fig.align = "center", echo=FALSE}
coffee_moisture <- coffee_ratings %>%
  select("total_cup_points","moisture","processing_method")

coffee_moisture %>%
filter(total_cup_points > 65) %>%
ggplot(aes(x = moisture , y = total_cup_points , color = processing_method)) +
 geom_point()
```

---

# Relationship between moisture and total cup points

```{r warning=FALSE, out.width="80%", fig.width=6, fig.align = "center", echo=FALSE}
coffee_moisture <- coffee_ratings %>%
  select("total_cup_points","moisture","processing_method")

coffee_moisture %>%
 filter(total_cup_points > 65) %>%
  ggplot(aes(x = moisture, y = total_cup_points, color = processing_method)) +
  geom_point(size = 0.5) +
  facet_wrap(~ processing_method, scale = "free_y") + 
  theme(legend.position = "none")
```

---

# Relationship between color and total cup points

```{r warning=FALSE, out.width="80%", fig.width=6, fig.align = "center", echo=FALSE}
coffee_color <- coffee_ratings %>%
  select("total_cup_points","color","processing_method")

coffee_color %>%
  filter(total_cup_points > 65) %>%
  ggplot(aes(total_cup_points, fill = color )) +
  geom_histogram(binwidth = 2) +
  facet_wrap(~ processing_method, scale = "free_y") + 
  theme(legend.position = "none")
```

---
class: inverse

# Conclusion

```{r echo = FALSE, out.width = "90%", fig.align = "center"}
include_graphics("http://m.qpic.cn/psc?/V10aRWDb4N6cVV/45NBuzDIW489QBoVep5mcf9iFDAWTU.ikJvUfQWIWe1lfKyPVZ5ydwbXZSo2YJKnlm15EkCmhFdRvDzHw9A9XAaI4DSmFGeFvglQUxhgAUs!/b&bo=4ANEAeADRAEBGT4!&rf=viewer_4&t=5")
```

---

class: inverse, middle, center

# Thanks for Watching